Nested sampling with multiple scalars

### 2015-10-04 Paper/ms.tex
Place to ramble about algorithm possibilities

The algorithm works as follows.

\section{Demonstration Example}
The prior is a uniform distribution over the $n$-dimensional unit hypercube:
\begin{eqnarray}
p(\xx) &=& 1
\end{eqnarray}
as long as $x_i \in [0, 1]$ for all $i$. The scalars are:
\begin{eqnarray}
S_1(\xx) &=& -\sum_{i=1}^n \left(x_i - 0.5\right)^2\\
S_2(\xx) &=& -\sum_{i=1}^n \sin^2\left(4\pi x_i\right)
\end{eqnarray}

For this section, we used $n=1000$ dimensions.

\section{Example: Potts model with some embellishments}

TBD

\section{A Diffusive Variant}

Have one walker, or a few (not a large number).

Explore the prior $\pi(\xx)$, and save sampled values of the scalars
(thinned, presumably). As a function of position $(s_1, s_2)$ there is a well
defined value of the cumulative prior mass
\begin{eqnarray}
M(s_1, s_2) &=& \int \pi(\xx)\mathds{1}\left(S_1(\xx) \leq s_1,
S_2(\xx) \leq s_2\right)\, d\xx
\end{eqnarray}
which can be approximated in a Monte Carlo fashion by
\begin{eqnarray}
\hat{M}(s_1, s_2) &=& \frac{1}{N}\sum_{i=1}^N \mathds{1}\left(S_1^i \leq s_1,
S_2^i \leq s_2\right)
\end{eqnarray}

>>>>

\section{Draft algorithm}

The algorithm works as follows.
Start with $N$ particles drawn from $\pi$.
Define the {\it corner count} of particle $i$ by
\begin{eqnarray}
C_i &=& \sum_{j=1}^N \mathds{1}\left(S_1^j < S_1^i, S_2^j < S_2^i\right)
\end{eqnarray}

Need to be able to sort particles into a total order. So add tiebreaker.
